%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
%---------------------------------------------------------
%---------------------------------------------------------

%---------------------------------------------------------    
    
  \cventry
    {Postdoctoral Research Fellow} % Job title
    {University of São Paulo} % Organization
    {São Carlos, Brazil} % Location
    {Sep. 2024 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mechatronics engineer working on the development of robotic frameworks for inspection and maintenance in oil platforms}
        \item {Technical leader of a team of 30-50 members and experienced in arranging international collaborations between universities}
        \item {Research in robotics, locomanipulation frameworks, and machine learning applications}
      \end{cvitems}
    }

  \cventry
    {Assistant Professor} % Job title
    {Faculty of Health Sciences, Albert Einstein Hospital} % Organization
    {São Paulo, Brazil} % Location
    {Jan. 2025 - Jul. 2025} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Assistant professor in the Biomedical Engineering Bachelor's program and in the Postgraduate Degree in Bioengineering Applied to Health.}
        % \item {Course: Processing of Biomedical Signals and Images.}
      \end{cvitems}
    }

  \cventry
    {Graduate Research Associate} % Job title
    {New Dexterity Research Group, The University of Auckland} % Organization
    {Auckland, New Zealand} % Location
    {Dec. 2021 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mechatronics engineer working on the development of novel human-machine interface solutions}
        \item {Development of novel bionic devices and deep learning algorithms}
      \end{cvitems}
    }
\vspace{-5pt} 

  \cventry
    {Research associate - Collaboration with Acumino (USA), part-time} % Job title
    {} % Organization
    {} % Location
    {Dec. 2021 - Aug. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Data collection and analysis of grasping and manipulation strategies using wearable human machine interfaces}
        \item {Development of machine learning-based algorithms for automated annotation of videos}
      \end{cvitems}
    }
\vspace{-5pt} 

  \cventry
    {Research associate - Collaboration with Prowood Limited (NZ), part-time} % Job title
    {} % Organization
    {} % Location
    {Sep. 2022 - Mar. 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Funded by the 2022/23 R\&D Experience Grants from Callaghan Innovation New Zealand's Innovation Agency}
        \item {Development of an automated framework for assembling beehive frames}
      \end{cvitems}
    }


%---------------------------------------------------------    
    
  \cventry
    {Graduate Research Associate} % Job title
    {University of São Paulo} % Organization
    {São Carlos, Brazil} % Location
    {Jul. 2019 - Jul. 2021} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Mechatronics engineer working on the development of novel deep learning and deep reinforcement learning techniques}
        \item {Member of the robotics surgery group}
        \item {Research in neurology, epilepsy, machine learning, and brain-machine interface}
      \end{cvitems}
    }
    

%---------------------------------------------------------
  \cventry
    {Undergraduate researcher - Fundação de Apoio à
Física e à Química (FAFQ)} % Job title
    {University of São Paulo} % Organization
    {São Carlos, Brazil} % Location
    {Jul. 2016 - Dec. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Engineering undergraduate researcher responsible for the development and implementation of an algorithm based on Dynamic Movement Primitives in a robotic arm. I also worked on the simulation of the autonomous vehicle using V-REP and ROS}
      \end{cvitems}
    }     
    

%---------------------------------------------------------
  \cventry
    {Engineering Intern} % Job title
    {MULTITTECH Engineering} % Organization
    {São Carlos, Brazil} % Location
    {Jan. 2019 - Jul. 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Intern in the modelling and simulation of dynamic systems group}
      \end{cvitems}
      }
      
%---------------------------------------------------------
  % \cventry
  %   {Undergraduate researcher - SENA Project} % Job title
  %   {University of São Paulo} % Organization
  %   {São Carlos, Brazil} % Location
  %   {Sep. 2016 - Jun. 2017} % Date(s)
  %   {
  %     \begin{cvitems} % Description(s) of tasks/responsibilities
  %       \item {Engineering undergraduate researcher responsible for the simulation of the autonomous vehicle using V-REP and Robot Operating System (ROS)}
  %     \end{cvitems}
  %   }       

\end{cventries}
%---------------------------------------------------------