%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects, Publications \& Courses}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Author of: “Helpo: an online platform for social purposes”} % Role
    {6th National Congress of Computer Engineering - Information Systems (CoNaIISI)} % Event
    {Mar del Plata, Argentina} % Location
    {Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {M.S. in Systems Engineering, Final degree project, UTN FRC}
        \item {Winner of the award: “Best community-chosen project” (Córdoba, 2018)}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Author of: “Investment project evaluation of a technological entrepreneurship for social purposes”} % Role
    {Bachelor of Business Administration} % Event
    {Cordoba, Argentina} % Location
    {Nov. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Licentiate degree in Business Administration, Final degree work, UNC FCE}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Duration: 24 hours. Information Systems Engineering Department of UTN FRC} % Role
    {Introduction to Business Intelligence course} % Event
    {Cordoba, Argentina} % Location
    {Aug. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {BI technologies: SSIS, SSAS, PowerBI, Kyubit}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Author of a business strategic consulting project} % Role
    {“Estrategias Cima S.A.” enterprise} % Event
    {Cordoba, Argentina} % Location
    {May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Final work of Strategic Management, B.B.A., UNC FCE}
      \end{cvitems}    
    }

%---------------------------------------------------------
  \cventry
    {Author of a business consulting project} % Role
    {“Cattaneo Hnos. S.R.L.” enterprise} % Event
    {Cordoba, Argentina} % Location
    {Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Final work of Administrative Systems and Procedures, B.B.A., UNC FCE}
      \end{cvitems}    
    }

%---------------------------------------------------------
  \cventry
    {Full-stack Developer} % Role
    {Web search engine using PageRank algorithm} % Event
    {Cordoba, Argentina} % Location
    {Jul. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Final work of Design of Query Languages, M.S. in Systems Engineering, UTN FRC}
      \end{cvitems}    
    }

%---------------------------------------------------------
  \cventry
    {Exhibitor} % Role
    {3rd Business Projects and Ideas Exhibition Day} % Event
    {Cordoba, Argentina} % Location
    {Aug. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s)}
        \item {Final work of Management Principles, B.B.A., UNC FCE}
      \end{cvitems}    
    }

%---------------------------------------------------------
\end{cventries}
