%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Publications}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cvparagraph}

\vspace{3pt} 

\scalebox{1.3}{\textbf{Journal Publications}}

B. Guan, Z. Wang, \textbf{R. V. Godoy}, M. Owen, and M. Liarokapis, "Combining Augmented Reality with Semi-autonomous, Lightmyography Based Control to Improve Usability of Prostheses", in IEEE Access, 2025 (under review).

B. Guan, \textbf{R. V. Godoy}, and M. Liarokapis, "On the Impact of Different Light Wavelengths in Decoding Grip Forces for Lightmyography Controlled Prosthetic Hands", in IEEE Access, 2025 (under review).

J. M. H. Pinheiro, S. V. B. de Oliveira, T. H. Segreto, P. A. R. Saraiva, E. F. de Souza, \textbf{R. V. Godoy}, L. A. Ambrosio, and M. Becker, \href{https://ieeexplore.ieee.org/document/11261543}{"The Impact of Feature Scaling In Machine Learning: Effects on Regression and Classification Tasks"}, in IEEE Access, 2025.


B. Guan, \textbf{R. V. Godoy}, M. Shahmohammadi, A. Dwivedi, and M. Liarokapis, \href{https://ieeexplore.ieee.org/abstract/document/10946889}{"Offline Versus Real-Time Grasp Prediction Employing a Wearable High-Density Lightmyography Armband: On the Control of Prosthetic Hands"}, in IEEE Access, 2025.

J. Buzzatto, H. Jiang, J. Liang, B. Busby, A. Lynch, \textbf{R. V. Godoy}, S. Matsunaga, R. Haraguchi, T. Mariyama, B. A. Macdonald, M. Liarokapis, \href{https://ieeexplore.ieee.org/abstract/document/10639969/}{"Multi-Layer, Sensorised Kirigami Grippers for Delicate yet Robust Robot Grasping and Single-Grasp Object Identification"}, in \textit{IEEE Access}, 2024.

\textbf{R. V. Godoy}, B. Guan, F. Sanches, A. Dwivedi and M. Liarokapis, \href{https://ieeexplore.ieee.org/document/10258264}{"Electromyography Based Gesture Decoding Employing Few-Shot Learning, Transfer Learning, and Training From Scratch"}, in \textit{IEEE Access}, 2023.

M. Shahmohammadi, B. Guan, \textbf{R. V. Godoy}, A. Dwivedi, P. Nielsen, and M. Liarokapis, \href{https://www.nature.com/articles/s41598-022-25982-w}{"On lightmyography based muscle-machine interfaces for the efficient decoding of human gestures and forces"}, in \textit{Nature Scientific Reports}, 2023.

\textbf{R. V. Godoy} et al., \href{https://ieeexplore.ieee.org/document/9834070}{"Electromyography-Based, Robust Hand Motion Classification Employing Temporal Multi-Channel Vision Transformers"}, in \textit{IEEE Robotics and Automation Letters (RA-L)}, 2022.

\textbf{R. V. Godoy}, A. Dwivedi and M. Liarokapis, \href{https://ieeexplore.ieee.org/document/9851477}{"Electromyography Based Decoding of Dexterous, In-Hand Manipulation Motions With Temporal Multichannel Vision Transformers"}, in \textit{IEEE Transactions on Neural Systems and Rehabilitation Engineering}, 2022.

\textbf{R. V. Godoy} et al., \href{https://ieeexplore.ieee.org/document/9889719}{"On EMG Based Dexterous Robotic Telemanipulation: Assessing Machine Learning Techniques, Feature Extraction Methods, and Shared Control Schemes"}, in \textit{IEEE Access}, 2022.

\vspace{5pt} 
\scalebox{1.3}{\textbf{Conference Publications}}

B. Guan, \textbf{R. V. Godoy}, A. Dwivedi, and M. Liarokapis, \href{https://www.researchgate.net/publication/394786098_On_the_Impact_of_Different_Light_Wavelengths_in_Decoding_Human_Intention_in_Lightmyography_Controlled_Prosthetic_Hands}{"On the Impact of Different Light Wavelengths in Decoding Human Intention in Lightmyography Controlled Prosthetic Hands"}, in 47th Annual International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC), 2025.

B. Guan, M. Kobayashi, \textbf{R. V. Godoy}, M. Owen, and M. Liarokapis, "On Semi-Autonomous, Intuitive, Lightmyography Based Control of Humanlike Robotic and Prosthetic Hands Utilizing Video and IMU Data
", in \textit{IEEE International Conference on BioInformatics and BioEngineering (BIBE)}, 2025.

R. R. Baptista, N. R. Gerszberg, \textbf{R. V. Godoy}, and G. J. G. Lahr, \href{https://arxiv.org/abs/2505.03929}{"MIHRaGe: A Mixed-Reality Interface for Human-Robot Interaction via Gaze-Oriented Control
"}, in \textit{IEEE International Conference on Advanced Robotics (ICAR)}, 2025.

M. V. da Silva, M. H. Carvalho, J. Negri, T. H. Segreto, \textbf{R. V. Godoy}, and M. Becker, \href{https://arxiv.org/abs/2508.14994}{"A Vision-Based Shared-Control Teleoperation Scheme for Controlling the Robotic Arm of a Four-Legged Robot
"}, \textbf{awarded the best paper} in the \textit{IEEE Latinamerican Robotics Symposium (LARS)}, 2025.

M. S. Tayar, L. K. de Oliveira, J. Negri, T. H. Segreto, \textbf{R. V. Godoy}, and M. Becker, \href{https://arxiv.org/abs/2508.16807}{"Autonomous UAV Flight Navigation in Confined Spaces: A Reinforcement Learning Approach
"}, in \textit{IEEE Latinamerican Robotics Symposium (LARS)}, 2025.

P. Saraiva, E. Ferreira, J. Pinheiro, T. H. Segreto, \textbf{R. V. Godoy}, and M. Becker, \href{https://arxiv.org/abs/2508.17468}{"A Synthetic Dataset for Manometry Recognition in Robotic Applications
"}, in \textit{IEEE Latinamerican Robotics Symposium (LARS)}, 2025.

D. Almeida, G. Lazzarini, J. Negri, T. H. Segreto, \textbf{R. V. Godoy}, and M. Becker, \href{https://arxiv.org/abs/2508.17466}{"Optimizing Grasping in Legged Robots: A Deep Learning Approach to Loco-Manipulation
"}, in \textit{IEEE Latinamerican Robotics Symposium (LARS)}, 2025.

\textbf{R. V. Godoy}, B. Guan, A. Dwivedi, M. Owen, and M. Liarokapis, \href{https://www.researchgate.net/publication/382596938_A_Video_Dataset_of_Everyday_Life_Grasps_for_the_Training_of_Shared_Control_Operation_Models_for_Myoelectric_Prosthetic_Hands}{"A Video Dataset of Everyday Life Grasps for the Training of Shared Control Operation Models for Myoelectric Prosthetic Hands
"}, in \textit{International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC)}, 2024.

\textbf{R. V. Godoy}, B. Guan, A. Dwivedi, and M. Liarokapis, \href{https://www.researchgate.net/publication/372861944_An_Affordances_and_Electromyography_Based_Telemanipulation_Framework_for_Control_of_Robotic_Arm-Hand_Systems}{"An Affordances and Electromyography Based Telemanipulation Framework for Control of Robotic Arm-Hand Systems
"}, in \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2023.

\textbf{R. V. Godoy}, B. Guan, A. Dwivedi, M. Shahmohammadi, M. Owen, and M. Liarokapis, \href{https://www.researchgate.net/publication/370770180_Multi-Grasp_Classification_for_the_Control_of_Robot_Hands_Employing_Transformers_and_Lightmyography_Signals}{"Multi-Grasp Classification for the Control of Robot Hands Employing Transformers and Lightmyography Signals"}, in \textit{International Conference of the IEEE Engineering in Medicine and Biology Society (EMBC)}, 2023.

B. Guan, \textbf{R. V. Godoy}, F. Sanches, A. Dwivedi, and M. Liarokapis, \href{https://www.researchgate.net/publication/372788367_On_Semi-Autonomous_Robotic_Telemanipulation_Employing_Electromyography_Based_Motion_Decoding_and_Potential_Fields}{"On Semi-Autonomous Robotic Telemanipulation Employing Electromyography Based Motion Decoding and Potential Fields"}, in \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2023.

M. Shahmohammadi, B. Guan, \textbf{R. V. Godoy}, and M. Liarokapis, \href{https://ieeexplore.ieee.org/document/10260643}{"An Adaptive, Humanlike Prosthetic Hand Equipped with a Series Elastic Differential and a Lightmyography Based Control Interface"}, in \textit{IEEE International Conference on Automation Science and Engineering (CASE)}, 2023.

B. Guan, \textbf{R. V. Godoy}, F. Sanches, A. Dwivedi, Y. Kwon, and M. Liarokapis, \href{https://www.researchgate.net/publication/370205435_Electromyography_and_Potential_Fields_Based_Shared_Control_Framework_for_Robotic_Telemanipulation}{"Electromyography and Potential Fields Based Shared Control Framework for Robotic Telemanipulation"}, in \textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2023.

N. Elangovan, \textbf{R. V. Godoy}, F. Sanches, K. Wang, T. White, P. Jarvis, and M. Liarokapis, \href{https://ieeexplore.ieee.org/document/10161171}{"On Human Grasping and Manipulation in Kitchens: Automated Annotation, Insights, and Metrics for Effective Data Collection"}, in \textit{IEEE International Conference on Robotics and Automation (ICRA)}, 2023.

J. Liang, J. Buzzatto, B. Busby, \textbf{R. V. Godoy}, S. Matsunaga, R. Haraguchi, T. Mariyama, B. Macdonald, M. Liarokapis, \href{https://www.researchgate.net/publication/374086867_Employing_Multi-Layer_Sensorised_Kirigami_Grippers_for_Single-Grasp_Based_Identification_of_Objects_and_Force_Exertion_Estimation?_tp=eyJjb250ZXh0Ijp7ImZpcnN0UGFnZSI6InByb2ZpbGUiLCJwYWdlIjoicHJvZmlsZSJ9fQ}{"Employing Multi-Layer, Sensorised Kirigami Grippers for Single-Grasp Based Identification of Objects and Force Exertion Estimation"}, in \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2023. 

F. Sanches, G. Gao, N. Elangovan, \textbf{R. V. Godoy}, J. Chapman, K. Wang, P. Jarvis, M. Liarokapis, \href{https://www.researchgate.net/publication/372861764_Scalable_Intuitive_Human_to_Robot_Skill_Transfer_with_Wearable_Human_Machine_Interfaces_On_Complex_Dexterous_Tasks}{"Scalable, Intuitive Human to Robot Skill Transfer with Wearable Human Machine Interfaces: On Complex, Dexterous Tasks"}, in \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2023.

\textbf{R. V. Godoy} et al., \href{https://ieeexplore.ieee.org/document/9925307}{"Electromyography-Based, Robust Hand Motion Classification Employing Temporal Multi-Channel Vision Transformers"}, in \textit{IEEE RAS/EMBS International Conference for Biomedical Robotics and Biomechatronics (BioRob)}, 2022.

\textbf{R. V. Godoy}, A. Dwivedi, M. Shahmohammadi and M. Liarokapis, \href{https://ieeexplore.ieee.org/document/9981514}{"Lightmyography Based Decoding of Human Intention Using Temporal Multi-Channel Transformers"}, in \textit{IEEE/RSJ International Conference on Intelligent Robots and Systems (IROS)}, 2022.

N. Elangovan, C. Chang, \textbf{R. V. Godoy}, F. Sanches, K. Wang, P. Jarvis, and M. Liarokapis, \href{https://ieeexplore.ieee.org/document/10000248}{"Comparing Human and Robot Performance in the Execution of Kitchen Tasks: Evaluating Grasping and Dexterous Manipulation Skills"}, in \textit{IEEE-RAS International Conference on Humanoid Robots (Humanoids)}, 2022.

\textbf{R. V. Godoy} et al., \href{https://ieeexplore.ieee.org/document/9529675}{"Redundant Robot Kinematics Error Analysis for Neurosurgical Procedures}", in \textit{IEEE International Conference on Industry Applications (INDUSCON)}, 2021.

L. A. Marão, L. Casteluci, \textbf{R. V. Godoy}, H. Garcia, D. V. Magalhães and G. Caurin, \href{https://ieeexplore.ieee.org/document/8981598}{"Deep Reinforcement Learning Control of an Autonomous Wheeled Robot in a Challenge Task: Combined Visual and Dynamics Sensoring"}, in \textit{International Conference on Advanced Robotics (ICAR)}, 2019.

\vspace{5pt} 
\scalebox{1.3}{\textbf{Preprint Publications}}

T.H. Segreto, J. Negri, P. H. Polegato, J. M. H. Pinheiro, \textbf{R. V. Godoy}, and M. Becker, \href{https://arxiv.org/abs/2503.01605}{"A Leaf-Level Dataset for Soybean-Cotton Detection and Segmentation"}, in ArXiV, 2025.

G. J. Lahr, \textbf{R. V. Godoy}, T. H. Segreto, J. O. Savazzi, A. Ajoudani, T. Boaventura, and G. A. Caurin, \href{https://arxiv.org/abs/2505.03917}{"Improving Failure Prediction in Aircraft Fastener Assembly Using Synthetic Data in Imbalanced Datasets"}, in ArXiv, 2025.

\textbf{R. V. Godoy} et al., \href{https://arxiv.org/abs/2209.11172}{"EEG-Based Epileptic Seizure Prediction Using Temporal Multi-Channel Transformers"}, in \textit{ArXiv}, 2022.




\end{cvparagraph}